\thispagestyle{plain} % Remove header
\addcontentsline{toc}{chapter}{General Conclusion}
\section*{General Conclusion}
The "Japan IT Skills System Simplified" project has made significant strides in addressing the challenges associated with the iCD toolset. By simplifying the toolset and developing a user-friendly web or mobile application, the project has enhanced the usability of the iCD toolset for IT recruiters and professionals.

The application has facilitated the creation of job descriptions, enabled the reevaluation of learning skills, and assisted in the reskilling, upskilling, and cross-skilling development process. The translation of the complex iCD data into a more accessible format and the automation of fetching relevant skills and tasks have further streamlined the process.

Despite the progress made, there were challenges encountered during the project. These included the complexity of the iCD toolset and the need for regular updates to keep the data current. However, these challenges were addressed through the use of various technologies and methodologies, demonstrating the project's adaptability and resilience.

Looking forward, there are several potential improvements and expansions to the project. These include further refining the user interface, integrating the application with existing HR systems, and expanding the scope to include other aspects of the iCD toolset. The project team is committed to continuing to enhance the application and contribute to the IT industry.

This project serves as a testament to the potential of simplifying complex toolsets and making them more accessible and useful. It is hoped that it will inspire further innovations in the field of IT recruitment and skill development.
